### 2021-03-18 paper.Rmd
adding dot points for discussion

* why tours are useful and what do we learn from them?
* what research is needed?

>>>>

* summarising the paper again
* highlighting the recent developments, spinifex, liminal, sage, slicing and sectioning, ferrn etc. 
* what's next - conditional model visualisation (Catherine Hurley's work), a interactive graphics system that easily integrates tours that provides the direct manipulations we want, pre-processing / transformations for high dimensional data, penalised projection pursuit, different kinds of data and spaces
